---
   title: "R test"  
   author: "Adam Pearce"  
   output:  
     html_document:  
       keep_md: true  

---
```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

Load data from URL
```{r}
require(data.table)
library(ggplot2)
library(dplyr)
library(stringr)

calls <- fread("../data/calls2.csv")
```


### Use dplyr mutate to add a time and length variable to each call
```{r}
calls <- calls %>%
  mutate(length = nchar(text)) %>%
  mutate(dateNum = as.numeric(year) + as.numeric(substr(x = quarter, start = 2, stop = 2))/4 - .25) %>%
  filter(dateNum < 2015.5) %>%
  filter(length > 0)
```


### Histogram of call lengths - I've filtered out 0 length calls
```{r}
ggplot(calls, aes(length)) + geom_histogram(binwidth=1000)
```


### Histogram of call quarter - not sure why the number falls off in 2010
there were also calls after 2016 - need to check the the parsing script is working
```{r}
ggplot(calls, aes(dateNum)) + geom_histogram(binwidth=.25)
```

### Scatter of quarter v length - looks like adverage length is decreasing
```{r}
ggplot(calls, aes(dateNum, length)) + geom_point() + geom_quantile(quantiles = c(.1, .25, .5, .75, .9))
```


### Violin of date v length - calls are getting shorter AND the number of very short calls is decreasing
```{r}
ggplot(calls, aes(year, length)) + geom_violin()
```


### Add a dummy variable counting millennial usage
```{r}
calls <- calls %>%
  mutate(wc = str_count(text, ignore.case("prosecute")))

byQ <- calls %>% 
  group_by(dateNum) %>% 
  summarize(length=sum(length), totalwc=sum(wc))
```

### Chart millennial word count over time
```{r}
ggplot(byQ, aes(dateNum, totalwc)) + geom_bar(stat='identity')

```

### Millenial density over time
```{r}
ggplot(byQ, aes(dateNum, totalwc/length)) + geom_bar(stat='identity')
```

### Millennial density when used
```{r}

```


### Number of docs using millennial over time
```{r}

```

### Density of docs using millennial over time
```{r}

```
